\documentclass[]{pavan}
\usepackage[framemethod=tikz]{mdframed}
\begin{document}

\namesection{Pavan Kumar}{Basheerabad}{
%\location{\qquad \qquad \qquad \qquad \quad \qquad \qquad  }
\href{mailto:pb14e@my.fsu.edu}{pb14e@my.fsu.edu} | +1 850-296-6465
}

\begin{center} 
\textit {Masters Graduate with 3+ years of Professional Experience in Business Intelligence and Data Warehousing. Proficient in PL/SQL, T-SQL, Designing ETL Mappings, Data Modeling, Creating BI Reports and Dashboards. Highly familiar with Cognos BI Administration, Architecture and Deployment.}
\end{center}

\vspace{-1em}
\noindent\fcolorbox{light-gray}{light-gray}{
\begin{minipage}[t]{0.31\textwidth} 

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!5]

\section{Areas of Expertise}
\vspace{\topsep}
\begin{tightemize}
\item Problem Solving
\item Data Analysis
\item Root Cause Analysis
\item Incident Management
\item Multi-tasking
\item Communication Skills
\item Troubleshooting
\item Research
\item Self-starter
\end{tightemize}
\end{mdframed}
\vspace{-1.13em}
\begin{mdframed}[hidealllines=true,backgroundcolor=gray!5]
\section{Skills}
\subsection{Languages}
SQL \textbullet{}   T-SQL \textbullet{} PL/SQL \textbullet{} C \textbullet{}   C++\\ Java 
\textbullet{} ASP .NET \textbullet{}   Python \\  UNIX Shell Scripting 

\sectionsep

\subsection{Databases}
Oracle 12c/11g/10g/9i \textbullet{} MySQL \\
SQL Server 2008 R2/2008/2005\\
DB2 \textbullet{} Microsoft Access

\sectionsep

\subsection{BI Tools}
IBM Cognos \textbullet{}   Business Objects  \\
SQL Server Reporting Services
\sectionsep
\subsection{ETL Tools}
IBM Datastage \textbullet{} Informatica\\
SQL Server Integration Services
\sectionsep

\subsection{Software}
TOAD \textbullet{} Microsoft Visual Studio\\
Microsoft Excel
\sectionsep

\subsection{Methodologies}
SDLC - Waterfall \textbullet{} Agile \textbullet{} Scrum
\end{mdframed}
\vspace{-1.13em}
\begin{mdframed}[hidealllines=true,backgroundcolor=gray!5]
\section{Education} 

\subsection{Florida State University}
\descript{Masters in Computer Science}
\location{Aug 2016 | Tallahassee, FL, USA \\ GPA: 3.68}
\sectionsep

\subsection{Sreenidhi Institute of}
\subsection{Science \& Technology}
\descript{Bachelors in Information}
\descript{Technology}
\location{Apr 2011 | Hyderabad, AP, INDIA}
\location{GPA: 3.2}
\end{mdframed}
\end{minipage} }
\noindent\fcolorbox{light-gray}{light-gray}{
\begin{minipage}[t]{0.64\textwidth} 
\begin{mdframed}[hidealllines=true,backgroundcolor=gray!5]
\section{Professional Work Experience}
\runsubsection{Tech Mahindra Ltd.}
\descript{| BI/ETL Developer}
\location{Sep 2011 - Jul 2014 | Hyderabad, AP, INDIA}
\begin{tightemize} 
\item Involved in the End-to-end Data warehouse design, creating facts and dimensions for building the Data warehouse application.
\item Collaborated with Business Analysts to gather requirements, Business rules and specifications to ensure reporting requirements are met.
\item Involved in all phases SDLC: Requirements Gathering, Analysis, Design, Implementation, Testing \& Deployment.

\item Developed and Implemented BI Reports using Cognos Report studio, Query Studio and Analysis Studio as per the Technical requirements.

\item Served as a primary point of contact by multi-tasking and taking accountability for Customer support environment issues including Operational, Application support and also providing end user support for reporting data solutions.

\item Extensively used Extract Transform Load (ETL) methodologies for Data extraction, Data Quality, Data Integrity, Data transformation and Data Processing using SQL Server Integration Services (SSIS) and Datastage.

\item Designed Data warehouse models – Star schema and Snowflake schema, facts, dimensions, cubes using Cognos Transformer.

\item Installed, configured, upgraded, maintained Cognos 8.4, Cognos 10.2.1 BI in a distributed windows environment.

\item Performed daily Cognos activities such as report/package/cube publishing, manage internal customer access and monitor schedules.

\item Proactively monitored application and troubleshooted any performance issues like High CPU Utilization, Disk Space utilization.

\item Worked with Database Administration team to understand and address Cognos BI reporting performance issues.

\end{tightemize}
\end{mdframed}
\vspace{-1.26em}
\begin{mdframed}[hidealllines=true,backgroundcolor=gray!5]
\section{Entry Level Training Program}
\runsubsection{Tech Mahindra Ltd.}
\descript{| BIDW Trainee}
\location{ May 2011 - Aug 2011 | Bhubaneswar, OR, INDIA}

\begin{tightemize}
\item Trained in courses like RDBMS, UNIX, Datawarehouse Concepts.
\item Acquired strong knowledge in Data warehousing and Business Intelligence by implementing case studies using Informatica and Business Objects.
\end{tightemize}
\end{mdframed}
\vspace{-1.26em}
\begin{mdframed}[hidealllines=true,backgroundcolor=gray!5]
\section{University Work Experience}
\runsubsection{Florida State University}
\descript{| Researcher/Teaching Assistant}
\location{ Jan 2015- Aug 2016 | Tallahassee, FL, USA}
\begin{tightemize}
\item Tweaked the java code to add new features to the Space Fortress game which helped in conducting experiments on Cognitive thinking.

\item Assisted in Troubleshooting UNIX Server Issues.

\item Involved in the Data Analysis of biological images by writing Python and UNIX Shell scripts.

\item Held help-lab hours for individual student consultations about assignments and grades related to Microsoft Office.

\end{tightemize}
\end{mdframed}

%\sectionsep


\end{minipage} }
\end{document}  \documentclass[]{article}